\mytitle

### 2016-11-05 pdocs/thesis/article-introduction.tex
article polishing

% !TeX root = article.tex
\begin{abstract}
We introduce simple and efficient method to simulate ductile fracture in existing physics engines.
Method is based on common technique of splitting bodies to multiple pieces.
\end{abstract}

@@

Plasticity is not typically taken into account in gaming solutions and 
destruction of various bodies often takes place based on collision or impulse exceeding predefined limit.
Nevertheless, breaking of steel or reinforced concrete structures using this approach 
is not appropriate if the simulation is to look realistic. Theory for handling of plasticity 
has been presented already in \cite{cg1988}. 
\cite{Jones:2016:EPD} provides extensive listing of related work during past decades.
\cite{muller2005meshless} 
present a method for modeling and animating of elastic and plastic bodies in real time using 
point based animation. This approach has not been widely used in computer games.  
One major issue is collision handling of deformable bodies.
Recently there has been multiple studies which have same target of bringing plasticity 
into main stream games as this work, \cite{Jones:2016:EPD,Patkar:2015:EDB,Budsberg:2014:EPD}.

>>>>

% !TeX root = article.tex
\begin{abstract}
We introduce simple and efficient method to simulate ductile fracture in existing physics engines.
Method is based on common technique of splitting bodies to multiple pieces and joining them with constraints.
Constraint behaviour is modelled using body dimensions and material parameters.
Sample program with full source code is made available to allow developers already using \cbullet\
to add plasticity into their simulations with minimal effort.
\end{abstract}

@@

Plasticity is not typically taken into account in gaming solutions and 
destruction of various bodies often takes place based on collision or impulse exceeding predefined limit.
Nevertheless, breaking of steel or reinforced concrete structures using this approach 
is not appropriate if the simulation is to look realistic. Theory for handling of plasticity 
has been presented already in \cite{cg1988}. 
\cite{Jones:2016:EPD} provides extensive listing of related work during past decades.
\cite{muller2005meshless} 
present a method for modeling and animating of elastic and plastic bodies in real time using 
point based animation. This approach has not been widely used in computer games.  
One major issue is collision handling of deformable bodies.
Recently there has been multiple studies which have same target of bringing plasticity 
into wider usage, \cite{Jones:2016:EPD,Patkar:2015:EDB,Budsberg:2014:EPD}.
Suggested methods seem best suited for film production and possible also for high end games.
Methodology presented in this study does not require significant software development efforts from
game vendors and is thus easily adoptable.
